Expos\'{e}\\ Proof of Vaccination on the Blockchain

### 2021-03-25 meeting-notes/2021-03-15-expose-vaccination.tex
update

The world is racing towards containing the Corona virus and fighting the pandemic.
One important step in this fight is to vaccinate as many people as possible.
At some point, it is expected that certain activities (e.g., air travel, cruises, sports) are only open to vaccinated  persons. To this end, there must be a central registry for all vaccinations so that everyone can proof their vaccination status.

@@

>>>>

The world is racing towards containing the Corona virus and fighting the pandemic.
One important step in this fight is to vaccinate as many people as possible.
At some point, it is expected that certain activities (e.g., air travel, cruises, sports) are open
exclusively to vaccinated  persons. To this end, there must be a central registry for all
vaccinations so that everyone can prove their vaccination status.

Trust is a major issue in this registry. Only certified authorities should be able to enter
vaccination records. It should not be possible to enter fake records. Each record should be linked
to an individual but without subverting data protection and privacy. Everyone
should be able to verify a vaccination given the identity of an individual within seconds.
A certified authority should be able to obtain the full record (which vaccine, when vaccinated)
within a reasonable time.

Entering records or obtaining a full record may incur a reasonable cost. Verifying a vaccination
should be as cheap as possible.

Authorities should be structured hierarchically. For example, there is a small number of worldwide
authorities; they vouch for national authorities, which in turn vouch for regional authorities and
then local authorities (e.g., doctors or vaccination centers). Such a structure is the standard for
certificates for webpages, emails, etc.

@@

The main concern is the cost to store the (huge) information on the blockchain and the cost and time
to verify.  So the most important task is to find out how to store and then verify the
vaccinations records with reasonable cost and time.
